What can GitHub and Googlecode Issues tell us about Exceptions in Android?

### 2014-08-26 android-stacks.tex
More improvements on introduction

The pervasiveness of the World Wide Web and the astonishing increase 
in the number of smartphones stimulated the creation of applications which extend the phones
 capabilities far beyond of the basic calls and textual messages.

If we look at global smartphone shipments the numbers are astoning;
the mobile industry shiped over 315 million smartphones in the last quarter of 2013.
Such increase on smartphones combined with the pervasiveness of the World Wide Web
 have stimulated the creation of applications which extend the phones capabilities 
far beyond of the basic calls and textual messages.

In this context, Android  leads the smartphone market, having over then 1 billion 
active users per month; thanks to its open-source model and hardware partners
 like Samsung, HTC, Motorola, Asus (besides Nexus its own device) [ref].

The number of apps built on top of Android increases in a daily rate <INCLUDE SOME STATISTICS>.

%If on the one hand such applications are getting mode and more popular....
%On the other hand... there is a need for realiability, as some core functionalities 
%are moving to apps....such applications impose more challenges to software reliability

%Such mobile platforms are intrinsically multi-threaded and support a development model 
% slightly (or sometimes drastically) different from those adopted on Web development [arie-icse],

%abnormal computation states

Such applications have to cope with an increasing number of abnormal
computation states, arising from: programmming errors (e.g. null dereferences);
 noisy user inputs; faults in underlying middleware or hardware; 
faults on third party services and libraries, compatibility issues [ref], 
conection with devices e.g., as GPS, camera, among others; memory and batery restrictions
among others.

Therefore, techniques for error detection and handling are not  an optional add-on but a 
fundamental part of such apps.
% as any other modern system~\cite{bruntink2006discovering}. 
The Android platform uses the exception handling mechanism embeeded
 in Java to deal with such conditions. Although the exception handling mechanism
~\cite{goodenough1975exception} is one of the most used schemes for
detecting and recovering from such exceptional conditions, studies (e.g.~\cite{miller1997issues,Robil00,shah2010understanding, garcia2007extracting,garcia2001comparative,cabral2007exception,coelho2011unveiling}),
have shown that it is generally poorly understood and the less tested parts of the system ~\cite{coelho2011unveiling}.
The consequence of the exception handling code may come the other way around making the code even less robust.

Our conjecture is that several Android applicatons may be suffering from similar vulnerabilities on the exception
handling code of the applications themselves or on the underlaying platform, and that such vulnerabiliries may be leading
 to application crashes.

Untill recent years, the availability of issues reporting abnormal
computation states (e.g., crashes) was scarce, while the
available data concerned a few large scale projects (e.g. the Mozilla
crash report dataset\footnote{https://code.google.com/p/promisedata/issues/detail?id=88}).
Along the recent years, we have witnessed a rapid increase in the number of open
source projects that make their control version and issue tracking systems
publicly available in repository hosting sites such as GitHub and Googlecode.

@@

<SUCH ISSUES INCLUDE STACK TRACES. WHAT IS THE RELATION BETWEEN STACK TRACE AND CRASH>
<stack traces are part of good issues....>
When available, such information can enable different kinds of post-mortem analysis, such as:
: classify .... (get from previous versions). Previous studies on crash report analysis focused a system 
at a time. Moreover, none of them target 
a family of Android applications (which share a common core) extracting the characteristics on exceptional issues 
and looking for similar vulnerabilities on applications and underlaying platform.

>>>>

Along the recent years, we have witnessed an astonishing increase in the number 
mobile applications available. Such increase is motivated by pervasiveness of the World Wide Web 
and the unprecedent increase of global smartphone shipments -
the mobile industry shiped over 315 million smartphones in the last quarter of 2013 [ref-IO].

%the mobile industry shiped over 315 million smartphones in the last quarter of 2013
%The pervasiveness of the World Wide Web and the astonishing increase 
%in the number of smartphones stimulated the creation of applications which extend the phones
% capabilities far beyond of the basic calls and textual messages. 
%f we look at global smartphone shipments the numbers are astoning;
%the mobile industry shiped over 315 million smartphones in the last quarter of 2013 [ref-googleIO].
%Such increase on smartphones combined with the pervasiveness of the World Wide Web
%have stimulated the creation of applications which extend the phones capabilities 
%far beyond of the basic calls and textual messages.

In this context, Android is currently the leading plaftorm of such applictions - thanks to its open-source 
model and hardware partners like Samsung, HTC, Motorola, Asus (besides Nexus its
 own device) [ref].  Google estimates that there is over 1 billion Android active users per month [ref-IO],
and the number of apps built on top of Android increases in a daily rate.

%If on the one hand such applications are getting mode and more popular....
%On the other hand... there is a need for realiability, as some core functionalities 
%are moving to apps....such applications impose more challenges to software reliability 
%Such mobile platforms are intrinsically multi-threaded and support a development model 
% slightly (or sometimes drastically) different from those adopted on Web development [arie-icse],  
%abnormal computation states

If on the one hand such applications extend the phones capabilities 
far beyond of the basic calls and textual messages, on the other hand
they have to face to new challenges imposed by mobile environmet.
Such applications have to cope with an increasing number of abnormal
computation states, arising from: programmming errors;
 noisy user inputs; faults in underlying middleware or hardware; 
faults on third party services and libraries, compatibility issues [ref], 
conection with devices e.g., as GPS, camera, memory and batery restrictions
among others.

Therefore, techniques for error detection and handling are not  an optional add-on but a 
fundamental part of such apps.
% as any other modern system~\cite{bruntink2006discovering}. 
The Android platform uses the exception handling mechanism embeeded
 in Java to deal with such conditions. Although the exception handling mechanism
~\cite{goodenough1975exception} is one of the most used schemes for
detecting and recovering from such exceptional conditions, studies (e.g.~\cite{miller1997issues,Robil00,shah2010understanding, garcia2007extracting,garcia2001comparative,cabral2007exception,coelho2011unveiling}),
have shown that it is generally poorly understood and the less tested parts of the system ~\cite{coelho2011unveiling}.
As a consequence that the exception handling code may become  ilself a source of faults, 
and may affect the system the other way around, making the system even less robust ~\cite{coelho2011unveiling}[ref FU CHEN].

In the same rathe the number of number of mobile appsincreases, also increases 
the number of users affected by their failures. Our conjecture is that several 
Android applicatons may be suffering from similar vulnerabilities on the exception 
handling code of the applications themselves or on the underlaying platform, and 
that such vulnerabiliries may be leading to application crashes.

Untill recent years, the availability of issues reporting abnormal
computation states (e.g., crashes) was scarce. The
available data comprised few large scale projects (e.g. the Mozilla
crash report dataset\footnote{https://code.google.com/p/promisedata/issues/detail?id=88}).
Recently we have observed a rapid increase in the number of open
source projects that make their control version and issue tracking systems
publicly available in repository hosting sites such as GitHub and Googlecode.

@@

<SUCH ISSUES INCLUDE STACK TRACES. WHAT IS THE RELATION BETWEEN STACK TRACE AND CRASH>
<stack traces are part of good issues....>

When available, crash-related information added on issues and crash reports can enable different kinds of post-mortem analysis, such as
 bug classification and clustering ~\cite{wang2013improving, kim2011crash, dhaliwal2011classifying},  the automated bug fixing ~\cite{sinha2009fault},  
fault-proneness prediction models ~\cite{kim2013predicting} and can also be used to support developers in debugging ~\cite{schroter2010stack}.

Previous studies on crash report analysis focused a system 
at a time. Moreover, none of them target a family of Android applications (which share a common core) extracting 
the characteristics on exceptional issues and looking for similar vulnerabilities on applications and underlaying platform.
